FM project

### 2023-05-15 draft1.tex
updated

\includegraphics{draft1_files/figure-latex/data_prep-1.pdf}
\textbf{Comment on Nat Gas export zeros}

@@

\includegraphics{draft1_files/figure-latex/time series overview-1.pdf}

@@

\includegraphics{draft1_files/figure-latex/overview by product-1.pdf}
\#\#\# 3. Time series decomposition \#\#\#\# 3.1. Adjustments

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(fpp3)}
\FunctionTok{library}\NormalTok{(tidyverse)}
\FunctionTok{library}\NormalTok{(ggplot2)}
\FunctionTok{library}\NormalTok{(dplyr)}
\FunctionTok{library}\NormalTok{(tidyr)}
\FunctionTok{library}\NormalTok{(lubridate)}
\FunctionTok{library}\NormalTok{(scales)}

\CommentTok{\#Total Crude Oil Exports by Destination}

\NormalTok{raw\_crude\_oil }\OtherTok{\textless{}{-}} \FunctionTok{read\_csv}\NormalTok{(}\StringTok{"https://raw.githubusercontent.com/edb{-}313/Energy{-}trade{-}forecasting/main/Data/csv/Total\%20Crude\%20Oil\%20Exports\%20by\%20Destination\_EIA.csv"}\NormalTok{, }\AttributeTok{skip =} \DecValTok{2}\NormalTok{,)}

\CommentTok{\#Leaving only country names in column names}

\FunctionTok{names}\NormalTok{(raw\_crude\_oil)[}\SpecialCharTok{{-}}\DecValTok{2}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{str\_replace\_all}\NormalTok{(}\FunctionTok{names}\NormalTok{(raw\_crude\_oil)[}\SpecialCharTok{{-}}\DecValTok{2}\NormalTok{],}
                                            \FunctionTok{c}\NormalTok{(}\StringTok{"U.S. Exports to "} \OtherTok{=} \StringTok{""}\NormalTok{,}
                                              \StringTok{" of Crude Oil }\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{(Thousand Barrels}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{)"} \OtherTok{=} \StringTok{""}\NormalTok{))}

\CommentTok{\#Pivoting (switching) columns starting from 2 column to rows}

\NormalTok{crude\_oil }\OtherTok{\textless{}{-}}\NormalTok{ raw\_crude\_oil }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \SpecialCharTok{{-}}\NormalTok{Date,}
               \AttributeTok{names\_to =} \StringTok{\textquotesingle{}Destination country\textquotesingle{}}\NormalTok{,}
               \AttributeTok{values\_to =} \StringTok{\textquotesingle{}Amount of Crude Oil (Thousand Barrels)\textquotesingle{}}\NormalTok{)}

\CommentTok{\#Filtering out values where Date is \textquotesingle{}NA\textquotesingle{}}

\NormalTok{crude\_oil }\OtherTok{\textless{}{-}}\NormalTok{ crude\_oil }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{drop\_na}\NormalTok{(Date) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{Date =} \FunctionTok{as.Date}\NormalTok{(Date))}

\CommentTok{\#Fixing date format, replacing \textquotesingle{}na\textquotesingle{} values with 0}

\NormalTok{crude\_oil}\SpecialCharTok{$}\NormalTok{Date }\OtherTok{\textless{}{-}} \FunctionTok{as.Date}\NormalTok{(crude\_oil}\SpecialCharTok{$}\NormalTok{Date)}
\NormalTok{crude\_oil}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Amount of Crude Oil (Thousand Barrels)}\StringTok{\textasciigrave{}} \OtherTok{\textless{}{-}} \FunctionTok{replace\_na}\NormalTok{(crude\_oil}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Amount of Crude Oil (Thousand Barrels)}\StringTok{\textasciigrave{}}\NormalTok{, }\DecValTok{0}\NormalTok{)}

\CommentTok{\#Setting up the tsibble}

\NormalTok{ts\_crude\_oil }\OtherTok{\textless{}{-}}\NormalTok{ crude\_oil }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{Date =} \FunctionTok{yearmonth}\NormalTok{(Date)) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{as\_tsibble}\NormalTok{(}
    \AttributeTok{index =}\NormalTok{ Date, }
    \AttributeTok{key =} \StringTok{\textasciigrave{}}\AttributeTok{Destination country}\StringTok{\textasciigrave{}}
\NormalTok{  )}

\CommentTok{\#OECD Europe Countries vector}

\NormalTok{oecd\_europe }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Austria"}\NormalTok{, }\StringTok{"Belgium"}\NormalTok{, }\StringTok{"Czech Republic"}\NormalTok{, }\StringTok{"Denmark"}\NormalTok{, }\StringTok{"Estonia"}\NormalTok{,}
                 \StringTok{"Finland"}\NormalTok{, }\StringTok{"France"}\NormalTok{, }\StringTok{"Germany"}\NormalTok{, }\StringTok{"Greece"}\NormalTok{, }\StringTok{"Hungary"}\NormalTok{, }\StringTok{"Iceland"}\NormalTok{,}
                 \StringTok{"Ireland"}\NormalTok{, }\StringTok{"Italy"}\NormalTok{, }\StringTok{"Latvia"}\NormalTok{, }\StringTok{"Lithuania"}\NormalTok{, }\StringTok{"Luxembourg"}\NormalTok{,}
                 \StringTok{"Netherlands"}\NormalTok{, }\StringTok{"Norway"}\NormalTok{, }\StringTok{"Poland"}\NormalTok{, }\StringTok{"Portugal"}\NormalTok{, }\StringTok{"Slovak Republic"}\NormalTok{,}
                 \StringTok{"Slovenia"}\NormalTok{, }\StringTok{"Spain"}\NormalTok{, }\StringTok{"Sweden"}\NormalTok{, }\StringTok{"Switzerland"}\NormalTok{, }\StringTok{"Turkey"}\NormalTok{,}
                 \StringTok{"United Kingdom"}\NormalTok{)}

\CommentTok{\#filtering out only relevant values}

\NormalTok{oecd\_crude\_oil }\OtherTok{\textless{}{-}}\NormalTok{ ts\_crude\_oil }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{filter}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Destination country}\StringTok{\textasciigrave{}} \SpecialCharTok{\%in\%}\NormalTok{ oecd\_europe) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{filter}\NormalTok{(Date }\SpecialCharTok{\textgreater{}=} \FunctionTok{as.Date}\NormalTok{(}\StringTok{"2014{-}04{-}15"}\NormalTok{), Date }\SpecialCharTok{\textless{}=} \FunctionTok{as.Date}\NormalTok{(}\StringTok{"2023{-}01{-}15"}\NormalTok{)) }

\NormalTok{oecd\_crude\_oil\_agg }\OtherTok{\textless{}{-}}\NormalTok{ oecd\_crude\_oil }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{index\_by}\NormalTok{(Date) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarize\_at}\NormalTok{(}\FunctionTok{vars}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Amount of Crude Oil (Thousand Barrels)}\StringTok{\textasciigrave{}}\NormalTok{), sum) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ungroup}\NormalTok{()}

\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}

\CommentTok{\#Total Oil Products Exports by Destination}

\NormalTok{raw\_oil\_prod }\OtherTok{\textless{}{-}} \FunctionTok{read\_csv}\NormalTok{(}\StringTok{"https://raw.githubusercontent.com/edb{-}313/Energy{-}trade{-}forecasting/main/Data/csv/Total\%20Oil\%20Products\%20Exports\%20by\%20Destination\_EIA.csv"}\NormalTok{,  }\AttributeTok{skip =} \DecValTok{2}\NormalTok{,)}

\FunctionTok{names}\NormalTok{(raw\_oil\_prod)[}\SpecialCharTok{{-}}\DecValTok{2}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{str\_replace\_all}\NormalTok{(}\FunctionTok{names}\NormalTok{(raw\_oil\_prod)[}\SpecialCharTok{{-}}\DecValTok{2}\NormalTok{],}
                                           \FunctionTok{c}\NormalTok{(}\StringTok{"U.S. Exports to "} \OtherTok{=} \StringTok{""}\NormalTok{,}
                                             \StringTok{" of Total Petroleum Products }\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{(Thousand Barrels}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{)"} \OtherTok{=} \StringTok{""}\NormalTok{))}
\NormalTok{oil\_prod }\OtherTok{\textless{}{-}}\NormalTok{ raw\_oil\_prod }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \SpecialCharTok{{-}}\NormalTok{Date,}
               \AttributeTok{names\_to =} \StringTok{\textquotesingle{}Destination country\textquotesingle{}}\NormalTok{,}
               \AttributeTok{values\_to =} \StringTok{\textquotesingle{}Amount of total Petroleum Porducts (Thousand Barrels)\textquotesingle{}}\NormalTok{)}

\NormalTok{oil\_prod}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Amount of total Petroleum Porducts (Thousand Barrels)}\StringTok{\textasciigrave{}} \OtherTok{\textless{}{-}} \FunctionTok{replace\_na}\NormalTok{(oil\_prod}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Amount of total Petroleum Porducts (Thousand Barrels)}\StringTok{\textasciigrave{}}\NormalTok{, }\DecValTok{0}\NormalTok{)}

\NormalTok{oil\_prod }\OtherTok{\textless{}{-}}\NormalTok{ oil\_prod }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{drop\_na}\NormalTok{(Date) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{Date =} \FunctionTok{as.Date}\NormalTok{(Date))}

\NormalTok{ts\_oil\_prod }\OtherTok{\textless{}{-}}\NormalTok{ oil\_prod }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{Date =} \FunctionTok{yearmonth}\NormalTok{(Date)) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{as\_tsibble}\NormalTok{(}
    \AttributeTok{index =}\NormalTok{ Date, }
    \AttributeTok{key =} \StringTok{\textasciigrave{}}\AttributeTok{Destination country}\StringTok{\textasciigrave{}}
\NormalTok{  )}

\NormalTok{oecd\_oil\_prod }\OtherTok{\textless{}{-}}\NormalTok{ ts\_oil\_prod }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{filter}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Destination country}\StringTok{\textasciigrave{}} \SpecialCharTok{\%in\%}\NormalTok{ oecd\_europe) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{filter}\NormalTok{(Date }\SpecialCharTok{\textgreater{}=} \FunctionTok{as.Date}\NormalTok{(}\StringTok{"2014{-}05{-}15"}\NormalTok{), Date }\SpecialCharTok{\textless{}=} \FunctionTok{as.Date}\NormalTok{(}\StringTok{"2023{-}01{-}15"}\NormalTok{))}

\NormalTok{oecd\_oil\_prod\_agg }\OtherTok{\textless{}{-}}\NormalTok{ oecd\_oil\_prod }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{index\_by}\NormalTok{(Date) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarize\_at}\NormalTok{(}\FunctionTok{vars}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Amount of total Petroleum Porducts (Thousand Barrels)}\StringTok{\textasciigrave{}}\NormalTok{), sum) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ungroup}\NormalTok{()}

\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\CommentTok{\#Reliance on Russian gas}

\NormalTok{raw\_rel\_rusoil }\OtherTok{\textless{}{-}} \FunctionTok{read\_csv}\NormalTok{(}\StringTok{"https://raw.githubusercontent.com/edb{-}313/Energy{-}trade{-}forecasting/main/Data/csv/Monthly\_Reliance\_on\_Russian\_Oil.csv"}\NormalTok{, }\AttributeTok{skip =} \DecValTok{1}\NormalTok{)}

\NormalTok{rel\_rusoil }\OtherTok{\textless{}{-}}\NormalTok{ raw\_rel\_rusoil }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \SpecialCharTok{{-}}\NormalTok{...}\DecValTok{1}\NormalTok{,}
               \AttributeTok{names\_to =} \StringTok{\textquotesingle{}Date\textquotesingle{}}\NormalTok{,}
               \AttributeTok{values\_to =} \StringTok{\textquotesingle{}Total Oil Imports from Russia / Total Oil Imports (\%)\textquotesingle{}}\NormalTok{)}

\NormalTok{rel\_rusoil }\OtherTok{\textless{}{-}}\NormalTok{ rel\_rusoil }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{rename}\NormalTok{(}\AttributeTok{Country =}\NormalTok{ ...}\DecValTok{1}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{Date =}\NormalTok{ lubridate}\SpecialCharTok{::}\FunctionTok{dmy}\NormalTok{(Date)) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{select}\NormalTok{(}\StringTok{"Date"}\NormalTok{,}\StringTok{"Country"}\NormalTok{,}\StringTok{"Total Oil Imports from Russia / Total Oil Imports (\%)"}\NormalTok{)}

\NormalTok{ts\_rel\_rusoil }\OtherTok{\textless{}{-}}\NormalTok{ rel\_rusoil }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{as\_tsibble}\NormalTok{(}
    \AttributeTok{index =}\NormalTok{ Date,}
    \AttributeTok{key =}\NormalTok{ Country)}

\NormalTok{oecd\_relrus }\OtherTok{\textless{}{-}}\NormalTok{ ts\_rel\_rusoil }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{filter}\NormalTok{(Country }\SpecialCharTok{\%in\%}\NormalTok{ oecd\_europe)}

\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\CommentTok{\#Total Natural Gas Exports by Destination}

\NormalTok{raw\_nat\_gas }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\StringTok{\textquotesingle{}https://raw.githubusercontent.com/edb{-}313/Energy{-}trade{-}forecasting/main/Data/csv/Natural\%20Gas\%20Exports\%20by\%20Country\_EIA.csv\textquotesingle{}}\NormalTok{,}\AttributeTok{header=}\ConstantTok{TRUE}\NormalTok{ , }\AttributeTok{check.names=}\ConstantTok{FALSE}\NormalTok{, }\AttributeTok{skip =} \DecValTok{2}\NormalTok{)}

\CommentTok{\# drop columns 2{-}3, 6{-}8, 54 and 57{-}72}
\NormalTok{raw\_nat\_gas }\OtherTok{\textless{}{-}} \FunctionTok{subset}\NormalTok{(raw\_nat\_gas, }\AttributeTok{select =} \SpecialCharTok{{-}}\FunctionTok{c}\NormalTok{(}\DecValTok{2}\SpecialCharTok{:}\DecValTok{3}\NormalTok{, }\DecValTok{6}\SpecialCharTok{:}\DecValTok{8}\NormalTok{,}\DecValTok{54}\NormalTok{, }\DecValTok{57}\SpecialCharTok{:}\DecValTok{72}\NormalTok{))}
\NormalTok{raw\_nat\_gas[}\FunctionTok{is.na}\NormalTok{(raw\_nat\_gas)] }\OtherTok{\textless{}{-}} \DecValTok{0}

\CommentTok{\#cimbining exports to the same countries}

\NormalTok{nat\_gas }\OtherTok{\textless{}{-}}\NormalTok{ raw\_nat\_gas }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{Mexico =} \StringTok{\textasciigrave{}}\AttributeTok{U.S. Natural Gas Pipeline Exports to Mexico (MMcf)}\StringTok{\textasciigrave{}} \SpecialCharTok{+} \StringTok{\textasciigrave{}}\AttributeTok{Liquefied U.S. Natural Gas Exports by Truck to Mexico (Million Cubic Feet)}\StringTok{\textasciigrave{}}\NormalTok{,}
         \AttributeTok{Canada =} \StringTok{\textasciigrave{}}\AttributeTok{U.S. Natural Gas Pipeline Exports to Canada (MMcf)}\StringTok{\textasciigrave{}} \SpecialCharTok{+} \StringTok{\textasciigrave{}}\AttributeTok{Liquefied U.S. Natural Gas Exports by Truck to Canada (Million Cubic Feet)}\StringTok{\textasciigrave{}}\NormalTok{)}

\CommentTok{\#removing duplicate columns}

\NormalTok{nat\_gas }\OtherTok{\textless{}{-}}\NormalTok{ nat\_gas[, }\SpecialCharTok{!}\NormalTok{(}\FunctionTok{names}\NormalTok{(nat\_gas) }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\StringTok{\textquotesingle{}U.S. Natural Gas Pipeline Exports to Mexico (MMcf)\textquotesingle{}}\NormalTok{,}
                                             \StringTok{\textquotesingle{}Liquefied U.S. Natural Gas Exports by Truck to Mexico (Million Cubic Feet)\textquotesingle{}}\NormalTok{,}
                                             \StringTok{\textquotesingle{}U.S. Natural Gas Pipeline Exports to Canada (MMcf)\textquotesingle{}}\NormalTok{,}
                                             \StringTok{\textquotesingle{}Liquefied U.S. Natural Gas Exports by Truck to Canada (Million Cubic Feet)\textquotesingle{}}\NormalTok{))]}

\CommentTok{\#cleaning column names}

\FunctionTok{colnames}\NormalTok{(nat\_gas) }\OtherTok{\textless{}{-}} \FunctionTok{gsub}\NormalTok{(}\AttributeTok{pattern =} \StringTok{".*(to}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{s)"}\NormalTok{, }\StringTok{""}\NormalTok{, }\FunctionTok{colnames}\NormalTok{(nat\_gas))}
\FunctionTok{colnames}\NormalTok{(nat\_gas) }\OtherTok{\textless{}{-}} \FunctionTok{gsub}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{(.*?}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{)"}\NormalTok{, }\StringTok{""}\NormalTok{, }\FunctionTok{colnames}\NormalTok{(nat\_gas))}

\CommentTok{\#pivoting data}
\NormalTok{gastemp }\OtherTok{\textless{}{-}}\NormalTok{ nat\_gas }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \SpecialCharTok{{-}}\NormalTok{Date,}
               \AttributeTok{names\_to =} \StringTok{\textquotesingle{}Destination country\textquotesingle{}}\NormalTok{,}
               \AttributeTok{values\_to =} \StringTok{\textquotesingle{}Amount of Natural gas (MMcf)\textquotesingle{}}\NormalTok{)}

\CommentTok{\#removing n/as in date column, fixing date formatting, fixing values (romoving space in the end)}
\FunctionTok{library}\NormalTok{(stringr) }\CommentTok{\#for triming the strings}

\NormalTok{gastemp }\OtherTok{\textless{}{-}}\NormalTok{ gastemp }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{drop\_na}\NormalTok{(Date) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{Date =} \FunctionTok{as.Date}\NormalTok{(Date)) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{mutate}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Destination country}\StringTok{\textasciigrave{}} \OtherTok{=} \FunctionTok{str\_trim}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Destination country}\StringTok{\textasciigrave{}}\NormalTok{))}

\CommentTok{\#summing duplicates }

\NormalTok{gastemp }\OtherTok{\textless{}{-}}\NormalTok{ gastemp }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{group\_by}\NormalTok{(Date, }\StringTok{\textasciigrave{}}\AttributeTok{Destination country}\StringTok{\textasciigrave{}}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarize\_at}\NormalTok{(}\FunctionTok{vars}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Amount of Natural gas (MMcf)}\StringTok{\textasciigrave{}}\NormalTok{), sum) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ungroup}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{drop\_na}\NormalTok{(Date)}

\CommentTok{\#creating a tsibble}

\NormalTok{ts\_nat\_gas }\OtherTok{\textless{}{-}}\NormalTok{ gastemp }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{Date =} \FunctionTok{yearmonth}\NormalTok{(Date)) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{as\_tsibble}\NormalTok{(}
    \AttributeTok{index =}\NormalTok{ Date,}
    \AttributeTok{key =} \StringTok{\textasciigrave{}}\AttributeTok{Destination country}\StringTok{\textasciigrave{}}
\NormalTok{  )}

\CommentTok{\#filtering only relevant data}

\NormalTok{oecd\_nat\_gas }\OtherTok{\textless{}{-}}\NormalTok{ ts\_nat\_gas }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{filter}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Destination country}\StringTok{\textasciigrave{}} \SpecialCharTok{\%in\%}\NormalTok{ oecd\_europe) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{filter}\NormalTok{(Date }\SpecialCharTok{\textgreater{}=} \FunctionTok{as.Date}\NormalTok{(}\StringTok{"2014{-}05{-}15"}\NormalTok{), Date }\SpecialCharTok{\textless{}=} \FunctionTok{as.Date}\NormalTok{(}\StringTok{"2023{-}01{-}15"}\NormalTok{))}

\NormalTok{oecd\_nat\_gas\_agg }\OtherTok{\textless{}{-}}\NormalTok{ oecd\_nat\_gas }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{index\_by}\NormalTok{(Date) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarize\_at}\NormalTok{(}\FunctionTok{vars}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Amount of Natural gas (MMcf)}\StringTok{\textasciigrave{}}\NormalTok{), sum) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ungroup}\NormalTok{()}

\NormalTok{oecd\_nat\_gas\_agg }\OtherTok{\textless{}{-}}\NormalTok{ oecd\_nat\_gas\_agg }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{mutate}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Amount of Natural gas (BOE)}\StringTok{\textasciigrave{}} \OtherTok{=} \StringTok{\textasciigrave{}}\AttributeTok{Amount of Natural gas (MMcf)}\StringTok{\textasciigrave{}} \SpecialCharTok{*} \DecValTok{1000} \SpecialCharTok{/} \DecValTok{6000}\NormalTok{ )}

\NormalTok{oecd\_nat\_gas\_agg }\OtherTok{\textless{}{-}}\NormalTok{ oecd\_nat\_gas\_agg }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{select}\NormalTok{(Date, }\StringTok{\textasciigrave{}}\AttributeTok{Amount of Natural gas (BOE)}\StringTok{\textasciigrave{}}\NormalTok{)}

\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}

\NormalTok{oecd\_merged }\OtherTok{\textless{}{-}} \FunctionTok{left\_join}\NormalTok{(oecd\_nat\_gas\_agg, oecd\_oil\_prod\_agg, }\AttributeTok{by =} \StringTok{"Date"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{left\_join}\NormalTok{(oecd\_crude\_oil\_agg, }\AttributeTok{by =} \StringTok{"Date"}\NormalTok{)}

\NormalTok{total\_exp\_oecd }\OtherTok{\textless{}{-}}\NormalTok{ oecd\_merged }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \SpecialCharTok{{-}}\NormalTok{Date, }\AttributeTok{names\_to =} \StringTok{"Export Type"}\NormalTok{, }\AttributeTok{values\_to =} \StringTok{"Amount"}\NormalTok{)}

\NormalTok{total\_exp\_oecd }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{ggplot}\NormalTok{(}
 \FunctionTok{aes}\NormalTok{(Date,Amount,}\AttributeTok{color =} \StringTok{\textasciigrave{}}\AttributeTok{Export Type}\StringTok{\textasciigrave{}}\NormalTok{)) }\SpecialCharTok{+}
   \FunctionTok{geom\_line}\NormalTok{()}\SpecialCharTok{+}
   \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Date"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Amount"}\NormalTok{)}\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"bottom"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics{draft1_files/figure-latex/data_prep-1} \end{center}

\textbf{Comment on Nat Gas export zeros}

@@

\begin{center}\includegraphics{draft1_files/figure-latex/time series overview-1} \end{center}

@@

\begin{center}\includegraphics{draft1_files/figure-latex/overview by product-1} \end{center}

\hypertarget{time-series-patterns}{%
\paragraph{2.3 Time Series Patterns}\label{time-series-patterns}}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# create seasonal plot of total exports monthly of Natural gas}
\NormalTok{total\_exp\_oecd }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Export Type}\StringTok{\textasciigrave{}} \SpecialCharTok{==} \StringTok{"Amount of Natural gas (BOE)"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{index\_by}\NormalTok{(Date) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{summarise}\NormalTok{(}\AttributeTok{Total\_Exports =} \FunctionTok{sum}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Amount}\StringTok{\textasciigrave{}}\NormalTok{)) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{gg\_season}\NormalTok{(Total\_Exports) }\SpecialCharTok{+}
  \FunctionTok{ylab}\NormalTok{(}\StringTok{"Total exports  of Natural Gas"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Seasonal plot: US exports of natural gas to OECD"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{labels =} \FunctionTok{comma\_format}\NormalTok{())}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics{draft1_files/figure-latex/Seasonal plot for each product-1} \end{center}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# create seasonal plot of total exports monthly of Crude oil}
\NormalTok{total\_exp\_oecd }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Export Type}\StringTok{\textasciigrave{}} \SpecialCharTok{==} \StringTok{"Amount of Crude Oil (Thousand Barrels)"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{index\_by}\NormalTok{(Date) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{summarise}\NormalTok{(}\AttributeTok{Total\_Exports =} \FunctionTok{sum}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Amount}\StringTok{\textasciigrave{}}\NormalTok{)) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{gg\_season}\NormalTok{(Total\_Exports) }\SpecialCharTok{+}
  \FunctionTok{ylab}\NormalTok{(}\StringTok{"Total exports  of Crude oil"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Seasonal plot: US exports of Crude Oil to OECD"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{labels =} \FunctionTok{comma\_format}\NormalTok{())}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics{draft1_files/figure-latex/Seasonal plot for each product-2} \end{center}
